# Exploring the Dataset 

```{r}
load(file.path("Data","training_2024-11-04.RData"))
SEPSISdat<-sepsis_data
load(file.path("Data","testing_2024-11-04.RData"))
nrow(SEPSISdat) # should be n=200112
SEPSISdat_test<-sepsis_data
rm("sepsis_data")
```


```{r}
id_sepsis<-unique(SEPSISdat$patient[SEPSISdat$SepsisLabel==1])
SEPSISdat$has_sepsis<-F
SEPSISdat$has_sepsis[SEPSISdat$patient %in% id_sepsis] <-T

SEPSISdat_NOsepsis <- SEPSISdat[!SEPSISdat$patient %in% unique(SEPSISdat$patient[SEPSISdat$SepsisLabel==1]),]
SEPSISdat_Sepsis <- SEPSISdat[SEPSISdat$patient %in% unique(SEPSISdat$patient[SEPSISdat$SepsisLabel==1]),]
SEPSISdat_Sepsis <- SEPSISdat_Sepsis[SEPSISdat_Sepsis$SepsisLabel==1,]
```

- Need to check features - map each column and the units they use using the paper
- We need to see literature to see which features which features have the greatest effects on sepsis 
- Need to do scaling for certain features 
- Possibly one hot encoding for some features 
- need to remove some features
- improve imputing strategies 
- Try different models 
- Do hyperparameter tuning 
- Could stack models 
- consider temporal based 